---
title: "Content Listing"
format: 
  html:
    theme: cosmo
    css: styles.css
    toc: true
    toc-depth: 2
execute:
    echo: false
---

## Public Access Content

```{r}
#| include: false
library(dplyr)
library(stringr)
library(connectapi)
library(DT)

# Get environment variables
server_url <- Sys.getenv("CONNECT_SERVER_URL")
api_key <- Sys.getenv("CONNECT_API_KEY")

# Validate environment variables
if (server_url == "" || api_key == "") {
  stop("Please set CONNECT_SERVER_URL and CONNECT_API_KEY environment variables")
}

client <- connect(
  server = server_url,
  api_key = api_key
)
```

```{r}
#| label: get-content
content <- get_content(client) |> 
    filter(access_type == 'all')
```

```{r}
#| label: create-table
#| output: asis
cat("<div class='content-table'>\n")
for (i in 1:nrow(content)) {
  cat(sprintf("<div class='content-item'>\n"))
  cat(sprintf("  <a href='%s' class='content-link'>%s</a>\n", 
              content$content_url[i], 
              content$title[i]))
  cat("</div>\n")
}
cat("</div>\n")
```

<style>
/* ECCB-inspired styling */
:root {
  --primary-color: #003366;
  --secondary-color: #0066cc;
  --background-color: #f5f5f5;
  --text-color: #333333;
}

body {
  font-family: 'Arial', sans-serif;
  line-height: 1.6;
  color: var(--text-color);
  background-color: var(--background-color);
  max-width: 1200px;
  margin: 0 auto;
  padding: 2rem;
}

h1, h2, h3 {
  color: var(--primary-color);
  border-bottom: 2px solid var(--secondary-color);
  padding-bottom: 0.5rem;
}

.content-table {
  background: white;
  border-radius: 8px;
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
  padding: 1.5rem;
  margin-top: 1.5rem;
  display: grid;
  grid-template-columns: repeat(3, 1fr);
  gap: 1rem;
}

.content-item {
  padding: 0.75rem;
  border: 1px solid #eee;
  border-radius: 4px;
  transition: all 0.3s ease;
  background: white;
}

.content-item:hover {
  background-color: #f8f9fa;
  transform: translateY(-2px);
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
}

.content-link {
  color: var(--primary-color);
  text-decoration: none;
  font-size: 1rem;
  display: block;
  transition: color 0.3s ease;
  line-height: 1.4;
}

@media (max-width: 1200px) {
  .content-table {
    grid-template-columns: repeat(2, 1fr);
  }
}

@media (max-width: 768px) {
  .content-table {
    grid-template-columns: 1fr;
  }
}
</style>
